---
title: "05312017_Kim.Seungmo"
output:  
  html_document:
    keep_md: yes
---

```{r include=FALSE}
library(tidyverse)
library(reshape2)
library(modelr)
```

#### 10.5 Exercises

1. How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).

```{r}
mtcars %>% is_tibble()

as.tibble(mtcars) %>% is_tibble()
```

    When we print a tibble, it only shows the first 10 rows and all the columns that fit on one screen. It also prints an abbreviated description of the column type.


2. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?
```{r}
df <- data.frame(abc = 1, xyz = "a")  
df
df$a # allows partial matching
df[, "xyz"]
df[, c("abc", "xyz")]
```

```{r}
df1 <- tibble(abc = 1, xyz = "a")
df1

# to extract a single column, use $ or [[ ]]
df1$abc # Tibbles do not allow partial matching(e.g. df$a)
df1[, "xyz"]
df1[["xyz"]]
df1[, c("abc", "xyz")]
```

    Honestly, I have not been frustrated in using data.frame yet...


3. If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?
```{r}
mpg
var <- "drv" # store driving mode(e.g. f=front-wheel) in a new variable var

mpg[var]
mpg[[var]]
mpg[,var]
```

4. Practice referring to non-syntactic names in the following data frame by:
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
annoying
```

  1. Extracting the variable called 1.
```{r}
annoying$`1` # variable named 1
annoying[, '1'] # variable named 1
annoying[, 1] # the 1st column
```

  2. Plotting a scatterplot of 1 vs 2.
```{r}
plot(annoying, 1, 2)  
```

  3. Creating a new column called 3 which is 2 divided by 1.
```{r}
annoying %>%
  mutate(`3` = `2` / `1`)
```


  4. Renaming the columns to one, two and three.

```{r}
annoying %>%
  mutate(`3` = `2` / `1`) %>%
  transmute('one' = `1`, `two` = `2`, `three` = `3`)
```


5. What does tibble::enframe() do? When might you use it?

    enframe() converts vectors or lists to two-column data frames. To create tibbles quickly and easily using vectors.
```{r}
enframe(1:3)
enframe(c(a=2, b=4, c=10))
```

    
6. What option controls how many additional column names are printed at the footer of a tibble?

```{r}
library(nycflights13)
is_tibble(flights)
flights # print the first 10 rows and the columns that fit on the screen by default, and show the other variables at the footer. 
options(tibble.max_extra_cols=5) # show only three other variables in the footer
flights
```

