---
title: "06072017_Kim.Seungmo"
output:
  html_document:
    keep_md: yes
---

```{r include=FALSE}
library(tidyverse)
library(readr)
```


```{r}
read_csv("a,b,c,
1,2,3,
4,5,6")
```
```{r}
read_csv("The first line of metadata
  The second line of metadata
  x,y,z
  1,2,3", skip = 2)

read_csv("# A comment I want to skip
  x,y,z
  1,2,3", comment = "#") # use comment = "#" to drop all lines that start with #.
```

```{r}
read_csv("1,2,3\n4,5,6", col_names = FALSE) # col_names=FALSE not to treat the first row as headings
read_csv("1,2,3\n4,5,6", col_names = c("x", "y", "z"))
read_csv("a,b,c\n1,2,.", na = ".")
```


#### 11.2.2 Exercises

1. What function would you use to read a file where fields were separated with “|”?

    read_delim(  ...  delim = "|")
    delim: single character used to separate fields within a record.
    read_csv(), read_tsv() and read_csv2() are special cases of the read_delim(). They are useful for
reading the most common types of rectangular-type(flat) data, comma, tab and ; separated values, respectively.  

2. Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?

    Many... for example,
    col_names: TRUE -> the first row of the input will be used as the column names, and will not be included in the data frame. If FALSE, column names will be generated automatically: X1, X2, X3 etc.
    locale: US-centric as default or create own locale such as time zone, encoding, decimal mark, big mark, and day/month names.
     

3. What are the most important arguments to read_fwf()?

    It's also very fast to parse, because every field is in the same place in every line. Need to describe the length of every field.
    col_positions	is important, created by fwf_empty(), fwf_widths() or fwf_positions(). To read in only selected fields, use fwf_positions().  
    
    
4. Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By convention, read_csv() assumes that the quoting character will be ", and if you want to change it you’ll need to use read_delim() instead. What arguments do you need to specify to read the following text into a data frame?
```{r}
read_csv("x,y\n1,'a,b'")
# maybe.. intended below
#  x    y
#  1  'a,b'
# But read_csv understand comma as a separator.
read_delim("x|y\n1|'a,b'", delim = "|") # argument _delim_ assigns a single character used to separate fields within a record.
```

5. Identify what is wrong with each of the following inline CSV files. What happens when you run the code?

```{r}
# read_csv() reads comma separated values in rectangular-type(flat) data!
read_csv("a,b\n1,2,3\n4,5,6") # numbers of columns are determined by columns in header -> 2x2

read_csv("a,b,c\n1,2\n1,2,3,4") # 2 x 3 
read_csv("a,b\n\"1") # 1x2
read_csv("a,b\n1,2\na,b") # correct! 2x2
read_csv("a;b\n1;3") #1x1
```


#### 11.3.5 Exercises

1. What are the most important arguments to locale()?

   I think _encoding_ is critical. This affects how the file is read. Default is UTF-8.
   
2. What happens if you try and set decimal_mark and grouping_mark to the same character? 
```{r}
# parse_number("123,456.78", locale = locale(grouping_mark = ".", decimal_mark = "."))
```

    decimal_mark and grouping_mark must be different!

What happens to the default value of grouping_mark when you set decimal_mark to “,”? 
```{r}
parse_number("123,456.78", locale = locale(decimal_mark = ","))
```
    
What happens to the default value of decimal_mark when you set the grouping_mark to “.”?
```{r}
parse_number("123,456.78", locale = locale(grouping_mark = "."))
```

    
3. I didn’t discuss the date_format and time_format options to locale(). What do they do? Construct an example that shows when they might be useful.

```{r}
# dt <- "2017-06-30 12:34:19"

# date_format(dt, "%M %D, %Y")
# , time_format = "%I:%M:%S")
```


4. If you live outside the US, create a new locale object that encapsulates the settings for the types of file you read most commonly.
```{r}
# parse_date("2016년 6월 30일", "%Y %B %D", locale = locale("kor"))
```


5. What’s the difference between read_csv() and read_csv2()?

    read_csv() reads the comma separated values and read_csv2() uses ; as seprator instead of comma. read_csv2() may be useful in the case of using comma as decimal separator(e.g. Germany)   
    
6. What are the most common encodings used in Europe? What are the most common encodings used in Asia? Do some googling to find out.

    UTF-8 - used in Linux by default, and much of the Internet
    UTF-16 - used by Windows, Mac OS X and Java programing  
    GB 18030 - used in China 
    EUC (Extended Unix Code) - EUC-JP(Japan) & EUC-KR(Korea)
    IEC 8859 series - used for most European languages


7. Generate the correct format string to parse each of the following dates and times:
```{r}
d1 <- "January 1, 2010"
parse_date(d1, "%B %D, %Y")

d2 <- "2015-Mar-07"
parse_date(d2, "%Y-%b-%d")

d3 <- "06-Jun-2017"
parse_date(d3, "%d-%b-%Y")

d4 <- c("August 19 (2015)", "July 1 (2015)")
parse_date(d4, "%B %d (%Y)")

d5 <- "12/30/14" 
parse_date(d5, "%m/%d/%y")

t1 <- "1705"
parse_time(t1, "%H%M")

t2 <- "11:15:10.12 PM"
parse_time(t2, "%I:%M:%S %p")
```

