--- 
title: "Ch5. Data Transformation(1)"
output:
  html_notebook: default
  html_document:
    keep_md: yes
  pdf_document: default
---
```{r include=FALSE}
library(nycflights13)
library(tidyverse)
```
\
  
  
#### 5.2.4 Exercises  

\ 

1. Find all flights that
\
a. Had an arrival delay of two or more hours
```{r}
filter(flights, arr_delay >= 2)
```
\
b. Flew to Houston (IAH or HOU)
```{r}
flights_departed <- filter(flights, !(is.na(dep_time))) # extract only the flights which left
filter(flights_departed, dest=="IAH" | dest=="HOU")
```
\
c. Were operated by United, American, or Delta
```{r}
filter(flights_departed, carrier=="UA" | carrier=="AA" | carrier=="DL")
filter(flights_departed, carrier %in% c("UA", "AA", "DL"))
```
\
d. Departed in summer (July, August, and September)
```{r}
filter(flights_departed, month == 7 | month == 8 | month == 9)
filter(flights_departed, month %in% c(7:9))
```
\
e. Arrived more than two hours late, but didn’t leave late
```{r}
filter(flights_departed, arr_delay > 120 & !(dep_delay > 0))
```
\
f. Were delayed by at least an hour, but made up over 30 minutes in flight
```{r}
filter(flights_departed, dep_delay >= 60 & (dep_delay - arr_delay) > 30)
```
\
g. Departed between midnight and 6am (inclusive)
```{r}
filter(flights_departed, !(dep_time > 0600 & dep_time < 2400))
```
\
2. Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?

\
between() is a shortcut for x >= left & x <= right

\
Departed in summer (July, August, and September)
```{r}
flights_departed[between(flights$month, 7, 9),]
```
\
Departed between midnight and 6am (inclusive)
```{r}
flights_departed[!(between(flights_departed$dep_time, 601, 2359)),]
flights_departed[!(between(flights_departed$dep_time, 601, 2359)),]
filter(flight, between(dep_time, 600, 2400))
```
\
3. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}
sum(is.na(flights$dep_time))
head(filter(flights, (is.na(dep_time))))
```
Missing dep_time means that the flight didn't depart. Therefore, the following variables do not exist in the flight.\
Dep_time, dep_delay, arr_time, arr_delay and air_time

\
4. Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)

```{r}
NA ^ 0 # (any numeric) ^ 0 always returns 1
```

```{r}
NA | TRUE  # '|' returns TRUE if either is TRUE and FALSE if both are FALSE.
NA | FALSE # returns the missing value because it is not the case above.
```

```{r}
FALSE & NA # '&' returns TRUE if both are TRUE and FALSE if either is FALSE.
TRUE & NA # returns the missing value becasue it is not the case above .
```
```{r}
NA * 0 # '*' requires two real numbers for the calculation
```
General rule) The calculation result including NA depends on each operator.

\


#### 5.3.1 Exercises

\
1. How could you use arrange() to sort all missing values to the start? (Hint: use is.na()).
```{r}
arrange(flights, is.na(dep_time)) # missing values to the end
arrange(flights, desc(is.na(dep_time))) # missing values to the start
```
\
2. Sort flights to find the most delayed flights. Find the flights that left earliest.
```{r}
arrange(flights_departed, desc(dep_delay))
arrange(flights_departed, dep_delay)
```
the most delayed flight: HA 51 departed 1301 min later than scheduled\
the flight that left earliest: B6 97 departed 43 min earlier than scheduled

\
3. Sort flights to find the fastest flights.
```{r}
arrange(flights_departed, desc(distance/air_time))
```
DL 1499 travelled 762 miles in 65 min.

\
4. Which flights travelled the longest? Which travelled the shortest?
```{r}
arrange(flights_departed, desc(distance))
arrange(flights_departed, distance)
```
The flights from JFK to HNL travelled 4983 miles.\
The flights from EWR to LGA travelled 80 miles.

\


#### 5.4.1 Exercises
\
1. Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.
```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)
select(flights, starts_with("dep"), starts_with("arr"))
```
\
2. What happens if you include the name of a variable multiple times in a select() call?
```{r}
select(flights, dep_time, dep_time)
```
The variable value is returned only once.
\
3. What does the one_of() function do? Why might it be helpful in conjunction with this vector?
```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights, one_of(vars))
```
one_of() selects variables in character vector.

\
4. Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?
```{r}
select(flights, contains("TIME")) # default: case insensitive
select(flights, contains("TIME", ignore.case = FALSE)) # case sensitive
```
default: ignore.case = TRUE

\


#### 5.5.2 Exercises
\
1. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
tempo <- mutate(flights,
  dep_minutes = dep_time %/% 100*60 + dep_time %% 100, 
  sched_dep_minutes = sched_dep_time %/% 100*60 + sched_dep_time %% 100) # convert into number of minutes  
select(tempo, dep_time, dep_minutes, sched_dep_time, sched_dep_minutes) # easy to calculate (in number of minutes)
```

\
2. Compare air_time with arr_time - dep_time. What do you expect to see? What do you see? What do you need to do to fix it?

```{r}
a <- transmute(flights, air_time, difference = arr_time - dep_time)

```
Dep_time and arv_time depend on the timezone of departure and arrival airport. So we need to convert dep_time and arr_time into standardized time by applying local time zone and Daylight Saving Time(DST)\
e.g. Davis UTC -7\
     New York UTC -4\
     London UTC -1
     
\
3. Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?
```{r}
transmute(flights, dep_time, sched_dep_time, dep_delay)
```
dep_delay = dep_time - sched_dep_time

\
4. Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for min_rank(). %>%
```{r}
arrange(flights, min_rank(desc(dep_delay)))
```
min_rank(): gives smallest values the small ranks, equivalent to rank(ties.method="min") 

\
5. What does 1:3 + 1:10 return? Why?
```{r}
1:3 + 1:10
```
The elements of the smaller vector are recycled until all elements of the longer vector are manipulated by the operator.

```{r}
1:3 + 1:9
```

\
6. What trigonometric functions does R provide?

Usage (x, y: numeric or complex vectors)

cos(x) cosine
sin(x) sine
tan(x) tangent

acos(x) arc-cosine
asin(x) arc-sine
atan(x) arc-tangent
atan2(y, x) two-argument arc-tangent

cospi(x) cos(pi*x)
sinpi(x) sin(pi*x)
tanpi(x) tan(pi*x)












