---
title: "08232017_Kim.Seungmo"
output:
  html_document:
    keep_md: yes
---

```{r include=FALSE}
library(tidyverse)
```

#### 19.5.5 Exercises

1. What does commas(letters, collapse = "-") do? Why?
```{r}
commas <- function(...) stringr::str_c(...) #default
commas(letters[1:5])

commas <- function(...) stringr::str_c(..., collapse = "-")
commas(letters[1:5])
# It return a-b-c-d-e.
```


2. It’d be nice if you could supply multiple characters to the pad argument, e.g. rule("Title", pad = "-+"). Why doesn’t this currently work? How could you fix it?
```{r}
rule <- function(..., pad = "-") {
  title <- paste0(...)
  width <- getOption("width") - nchar(title) - 5
  cat(title, " ", stringr::str_dup(pad, width), "\n", sep = "")
}
rule("Important output", pad = "+-*") # ??????? It works!
```


3. What does the trim argument to mean() do? When might you use it?
```{r}
x <- c(0:10, 50)
xm <- mean(x)
c(xm, mean(x, trim = 0)) # no trim
c(xm, mean(x, trim = 0.1)) # a symmetrically trimmed mean is computed with a fraction of trim observations deleted from each end before the mean is computed: 0 and 50 have been trimmed.
# Useful when endpoints might be noisy..
```

4. The default value for the method argument to cor() is c("pearson", "kendall", "spearman"). What does that mean? What value is used by default?
```{r}
# a character string indicating which correlation coefficient is to be computed. 
# default: pearson
```

Correlation is a bivariate analysis that measures the strengths of association between two variables and the direction of the relationship. 

**Pearson r correlation** is the most widely used correlation statistic to measure the degree of the relationship between linearly related variables.<br />
e.g. Is there a statistically significant relationship between age(in years), and height(in inches)?<br />
**Kendall rank correlation**: Kendall rank correlation is a non-parametric test that measures the strength of dependence between two variables.<br />
**Spearman rank correlation** is a non-parametric test that is used to measure the degree of association between two variables.<br />
e.g. Is there a statistically significant relationship between how the horses rank in the race and the horses’ ages?
<br />
<br />

#### 20.3.5 Exercises

1. Describe the difference between is.finite(x) and !is.infinite(x).
```{r}
#is.finite and is.infinite return a vector of the same length as x, indicating which elements are finite or infinite.
x <- c(530,Inf,NA)
is.finite(x)
is.infinite(x) # NA is neither finite nor infinite.
!is.infinite(x)
```

2. Read the source code for dplyr::near() (Hint: to see the source code, drop the ()). How does it work?
```{r}
dplyr::near
# if the difference between x and y is less than a tolerance level

sqrt(2) ^ 2 == 2 #sqrt(2) = 1.414214.......
near(sqrt(2) ^ 2, 2)
```


3. A logical vector can take 3 possible values. How many possible values can an integer vector take? How many possible values can a double take? Use google to do some research.

????? No idea..

4. Brainstorm at least four functions that allow you to convert a double to an integer. How do they differ? Be precise.

???? 

5. What functions from the readr package allow you to turn a string into logical, integer, and double vector?
```{r}
library(readr)

x <- c("TRUE","FALSE", "NA")
typeof(x)
typeof(parse_logical(x))

x <- c("1", "2", "3")
typeof(x)
typeof(parse_integer(x))

x <- c("1.23", "2.13", "3.12")
typeof(x)
typeof(parse_double(x))
```

