---
title: "09132017_Kim.Seungmo"
output:
  html_document:
    keep_md: yes
---

```{r include=FALSE}
library(tidyverse)
```

 
21.4.1 Exercises

1. Read the documentation for apply(). In the 2d case, what two for loops does it generalise?

double loops..it means there is a nested for loop in loop.

2. Adapt col_summary() so that it only applies to numeric columns You might want to start with an is_numeric() function that returns a logical vector that has a TRUE corresponding to each numeric column.?????????
```{r}
col_summary <- function(df, fun) {
  out <- vector("double", length(df))
  out_col <- vector("double", length(df))
  for (i in seq_along(df)) {
    out[i] <- fun(df[[i]])
  }
  out
}
col_summary(nycflights13::flights, is.numeric)
```

21.5.3 Exercises

1. Write code that uses one of the map functions to:

  1.Compute the mean of every column in mtcars.
```{r}
map_dbl(mtcars, mean)
```

  2.Determine the type of each column in nycflights13::flights.
```{r}
map_chr(nycflights13::flights, typeof)
```

  3.Compute the number of unique values in each column of iris.
```{r}
map_dbl(mtcars, function(x) length(unique(x)))
```

  4.Generate 10 random normals for each of μ=-10, 0, 10 and 100.
```{r}
map(c(-10, 0, 10, 100), function(x) rnorm(10, x))
```

 
2. How can you create a single vector that for each column in a data frame indicates whether or not it’s a factor?
```{r}

```

3.What happens when you use the map functions on vectors that aren’t lists? What does map(1:5, runif) do? Why?
```{r}
map(1:5, runif)

```


4.What does map(-2:2, rnorm, n = 5) do? Why? What does map_dbl(-2:2, rnorm, n = 5) do? Why?
```{r}
mtcars %>% map(sum) #return a list
mtcars %>% map_dbl(sum) #return a double vector

map(-2:2, rnorm, n = 5) 
#map_dbl(-2:2, rnorm, n = 5) #return a double vector

#e.g.
1:10 %>%
  map(rnorm, n = 10) %>%
  map_dbl(mean)
```


5.Rewrite map(x, function(df) lm(mpg ~ wt, data = df)) to eliminate the anonymous function.
```{r eval=FALSE}
# If we choose not to give the function a name, we get an anonymous function.
#1) give it a name -> quite verbose!
linear_model <- map(x, function(df) lm(mpg ~ wt, data = df))
map(mtcars)
map(x, function(df) linear_model(df))
map(mtcars)
#2)
(function(x) mtcars) ()
models <- mtcars %>% 
  split(.$cyl) %>% 
  map(~lm(mpg ~ wt, data = .))
```

21.9.3 Exercises

1. Implement your own version of every() using a for loop. Compare it with purrr::every(). What does purrr’s version do that your version doesn’t?
```{r}
x <- list(1:5, 2:9)
y <- list(0:10, c("a", "b", "c"))

x %>% every(is.numeric)
y %>% every(is.numeric)

count <- 0
for (val in x) {
    if(is.numeric(val))   count = count + 1
}
print(count)

sums <- 0
for (val in x) {
  print(sums)
  sums <- (sums + val)
  print(sums)
}


x <- list(0:10, 1000)
y <- list(0:10, c("a", "b", "c"))
x %>% every(is.numeric)
y %>% every(is.numeric)
#return TRUE or FALSE if every elements of a list satisfy a predicate

# every() equally treat every elements of a list but for loop doesn't
```

2. Create an enhanced col_sum() that applies a summary function to every numeric column in a data frame.
```{r}
col_sum <- function(df) {
  df[sapply(df, class) == 'numeric', ] %>%
   summary()
}

col_sum(nycflights13::flights)
```

3. A possible base R equivalent of col_sum() is:
```{r}
col_sum3 <- function(df, f) {
  is_num <- sapply(df, is.numeric)  
  df_num <- df[ ,is_num]

  sapply(df_num, f)
}
```


But it has a number of bugs as illustrated with the following inputs:
```{r}
df <- tibble(
  x = 1:3, 
  y = 3:1,
  z = c("a", "b", "c")
)

col_sum3(df, mean) #ok

# Has problems: don't always return numeric vector
col_sum3(df[1:2], mean)
col_sum3(df[1], mean)
#col_sum3(df[0], mean) #problematic
```

```{r eval=FALSE}
df2 <- data.frame(
  x = 1:3, 
  y = 3:1,
  z = c("a", "b", "c")
)
col_sum3(df2, mean) 
col_sum3(df2[1:2], mean)
col_sum3(df2[1], mean)
col_sum3(df2[0], mean) #problematic
```

What causes the bugs?





