---
title: "09062017_Kim.Seungmo"
output:
  html_document:
    keep_md: yes
---

```{r include=FALSE}
library(tidyverse)
```
21.2.1 Exercises

1.Write for loops to:

  1.Compute the mean of every column in mtcars.
```{r}
n <- ncol(mtcars)
for (i in 1:n) {
  print(colnames(mtcars[i]))
  print(mean(mtcars[,i]))
}
```

  2.Determine the type of each column in nycflights13::flights.
  3.Compute the number of unique values in each column of iris.
  4.Generate 10 random normals for each of μ=10, 0, 10 and 100. 
 
 

21.4.1 Exercises

1. Read the documentation for apply(). In the 2d case, what two for loops does it generalise?
```{r}

```

2. Adapt col_summary() so that it only applies to numeric columns You might want to start with an is_numeric() function that returns a logical vector that has a TRUE corresponding to each numeric column.
```{r}

```

21.5.3 Exercises

1. Write code that uses one of the map functions to:

  1.Compute the mean of every column in mtcars.
```{r}
map_dbl(mtcars, mean)
```

  2.Determine the type of each column in nycflights13::flights.
```{r}
map_chr(nycflights13::flights, typeof)
```

  3.Compute the number of unique values in each column of iris.
```{r}
map_dbl(mtcars, function(x) length(unique(x)))
```

  4.Generate 10 random normals for each of μ=-10, 0, 10 and 100.
```{r}
map(c(-10, 0, 10, 100), function(x) rnorm(10, x))
```

 
2. How can you create a single vector that for each column in a data frame indicates whether or not it’s a factor?
```{r}

```

3.What happens when you use the map functions on vectors that aren’t lists? What does map(1:5, runif) do? Why?
```{r}
map(1:5, runif)

```


4.What does map(-2:2, rnorm, n = 5) do? Why? What does map_dbl(-2:2, rnorm, n = 5) do? Why?
```{r}
map(-2:2, rnorm, n = 5)
#map_dbl(-2:2, rnorm, n = 5)
```


5.Rewrite map(x, function(df) lm(mpg ~ wt, data = df)) to eliminate the anonymous function.
```{r}
#map(mtcars, function(df) lm(mpg ~ wt, data = df))
```

21.9.3 Exercises

1. Implement your own version of every() using a for loop. Compare it with purrr::every(). What does purrr’s version do that your version doesn’t?

2. Create an enhanced col_sum() that applies a summary function to every numeric column in a data frame.
```{r}
col_sum <- function(df) {
  df[sapply(df, class) == 'numeric', ] %>%
   summary()
}

col_sum(nycflights13::flights)
```

3. A possible base R equivalent of col_sum() is:
```{r}
#col_sum3 <- function(df, f) {
#  is_num <- sapply(df, is.numeric)  
#  df_num <- df[ ,is_num]

#  sapply(df_num, f)
#}
#col_sum3(mtcars, mpg)

#But it has a number of bugs as illustrated with the following inputs:
df <- tibble(
  x = 1:3, 
  y = 3:1,
  z = c("a", "b", "c")
)

#col_sum3(df, mean) # OK
# Has problems: don't always return numeric vector
#col_sum3(df[1:2], mean)
#col_sum3(df[1], mean)
#col_sum3(df[0], mean)
```
What causes the bugs?





