---
title: "R Notebook"
output: html_notebook
          keep_md: true
---
```{r}
library(nycflights13)
library(tidyverse)
```

### 5.6 Grouped summaries with summarise()
```{r}
summarise(flights, delay = mean(dep_delay, na.rm = TRUE))
```
```{r grouped_summary}
by_day <- group_by(flights, year, month, day)
summarise(by_day, delay = mean(dep_delay, na.rm = TRUE)) # get the average delay per date
```
#### 5.6.1 Combining multiple operations with the pipe
To explore the relationship between the distance and average delay for each location.
```{r}
by_dest <- group_by(flights, dest)
delay <- summarise(by_dest,
  count = n(),
  dist = mean(distance, na.rm = TRUE),
  delay = mean(arr_delay, na.rm = TRUE))
(delay <- filter(delay, count > 20, dest != "HNL"))
```
```{r}
# It looks like delays increase with distance up to ~750 miles 
# and then decrease. Maybe as flights get longer there's more 
# ability to make up delays in the air?
ggplot(delay, aes(x = dist, y = delay)) +
  geom_point(aes(size = count), alpha = 1/3) +
  geom_smooth(se = FALSE)
```

```{r}
  group_by(flights, dest) %>% 
  summarise(
    count = n(),
    dist = mean(distance, na.rm = TRUE),
    delay = mean(arr_delay, na.rm = TRUE)
  ) %>% 
  filter(count > 20, dest != "HNL")
```
#### 5.6.2 Missing values

Without na.rm = TRUE
The usual rule of missing values: if there’s any missing value in the input, the output will be a missing value.
```{r}
flights %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay))
```
With na.rm = TRUE which removes the missing values prior to computation
```{r}
flights %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay, na.rm = TRUE))
```
To save a data set of not_cancelled
```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(mean = mean(dep_delay))
```

#### 5.6.3 Counts
To look at the planes (identified by their tail number) that have the highest average delays:
```{r}
delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  summarise(delay = mean(arr_delay))

ggplot(data = delays, mapping = aes(x = delay)) + 
  geom_freqpoly(binwidth = 10)
```
To draw a scatterplot of number of flights vs. average delay:
```{r}
delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  summarise(
    delay = mean(arr_delay, na.rm = TRUE),
    n = n()
  )

ggplot(data = delays, mapping = aes(x = n, y = delay)) + 
  geom_point(alpha = 1/10)
```
To filter out the groups with the smallest numbers of observations, so you can see more of the pattern and less of the extreme variation in the smallest groups. 
```{r}
delays %>% 
  filter(n > 25) %>% 
  ggplot(mapping = aes(x = n, y = delay)) + 
    geom_point(alpha = 1/10)
```
### 5.6.4 Useful summary functions

```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    avg_delay1 = mean(arr_delay),
    avg_delay2 = mean(arr_delay[arr_delay > 0]) # the average positive delay
  )
```

```{r}
# Why is distance to some destinations more variable than to others?
not_cancelled %>% 
  group_by(dest) %>% 
  summarise(distance_sd = sd(distance)) %>% 
  arrange(desc(distance_sd))
```

```{r}
# When do the first and last flights leave each day?
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    first = min(dep_time),
    last = max(dep_time)
  )
```

```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    first_dep = first(dep_time), 
    last_dep = last(dep_time)
  )
```


```{r}
not_cancelled %>% 
  group_by(year, month, day) %>% 
  mutate(r = min_rank(desc(dep_time))) %>% 
  filter(r %in% range(r))
```

```{r}
# Which destinations have the most carriers?
not_cancelled %>% 
  group_by(dest) %>% 
  summarise(carriers = n_distinct(carrier)) %>%  # to count the number of distinct values
  arrange(desc(carriers))
```

```{r}
not_cancelled %>% 
  count(dest)

not_cancelled %>% 
  count(tailnum, wt = distance)
```

```{r}
# How many flights left before 5am? (these usually indicate delayed
# flights from the previous day)
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(n_early = sum(dep_time < 500))
```

```{r}
# What proportion of flights are delayed by more than an hour?
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(hour_perc = mean(arr_delay > 60))
```
### 5.6.5 Grouping by multiple variables

When you group by multiple variables, each summary peels off one level of the grouping. That makes it easy to progressively roll up a dataset:

```{r}
daily <- group_by(flights, year, month, day)
(per_day   <- summarise(daily, flights = n()))
```

```{r}
(per_month <- summarise(per_day, flights = sum(flights)))
(per_year  <- summarise(per_month, flights = sum(flights)))
```
### 5.6.6 Ungrouping

If you need to remove grouping, and return to operations on ungrouped data, use ungroup().

```{r}
daily %>% 
  ungroup() %>%             # no longer grouped by date
  summarise(flights = n())  # all flights
```
### 5.6.7 Exercises

**1. Brainstorm at least 5 different ways to assess the typical delay characteristics of a group of flights. Consider the following scenarios:

. A flight is 15 minutes early 50% of the time, and 15 minutes late 50% of the time.

. A flight is always 10 minutes late.

. A flight is 30 minutes early 50% of the time, and 30 minutes late 50% of the time.

. 99% of the time a flight is on time. 1% of the time it’s 2 hours late.

Which is more important: arrival delay or departure delay?##

2. Come up with another approach that will give you the same output as not_cancelled %>% count(dest) and not_cancelled %>% count(tailnum, wt = distance) (without using count()).
```{r}
not_cancelled %>% count(dest)

not_cancelled %>% group_by(dest) %>% summarize(n=n())
```
```{r}
not_cancelled %>% count(tailnum, wt = distance)

not_cancelled %>% group_by(tailnum) %>% tally(wt=distance) # tally is to summarize that will either call n or sum(n)
```

3. Our definition of cancelled flights (is.na(dep_delay) | is.na(arr_delay) ) is slightly suboptimal. Why? Which is the most important column?

arr_delay is the key column. We sometimes see an airplane that departs but does not arrive.

4. Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?
```{r}
cancelled_per_day <- flights %>% group_by(year,month,day) %>%
  summarize(num_per_day=n(), 
            cancelled=sum(is.na(arr_delay)),
            perc_cancelled=cancelled/num_per_day,
            mean_arr_delay=mean(arr_delay,na.rm=TRUE))
cancelled_per_day
ggplot(data = cancelled_per_day, aes(x=mean_arr_delay, y=perc_cancelled)) + geom_point() + geom_smooth(method=lm, se=FALSE) 
```

5. Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about flights %>% group_by(carrier, dest) %>% summarise(n()))
```{r}
delayed <- filter(not_cancelled, arr_delay > 0) # extract the flights delayed
delayed %>% group_by(carrier) %>% summarize(delay_carrier=n()) %>% arrange(desc(delay_carrier))
delayed %>% group_by(origin) %>% summarize(delay_airport=n()) %>% arrange(desc(delay_airport))
```

6. What does the sort argument to count() do. When might you use it?
```{r}
not_cancelled %>% count(dest, sort = TRUE)
```

#### 5.7.1 Exercises

1. Refer back to the lists of useful mutate and filtering functions. Describe how each operation changes when you combine it with grouping.

2. Which plane (tailnum) has the worst on-time record?

3. What time of day should you fly if you want to avoid delays as much as possible?

4. For each destination, compute the total minutes of delay. For each, flight, compute the proportion of the total delay for its destination.

5. Delays are typically temporally correlated: even once the problem that caused the initial delay has been resolved, later flights are delayed to allow earlier flights to leave. Using lag() explore how the delay of a flight is related to the delay of the immediately preceding flight.

6. Look at each destination. Can you find flights that are suspiciously fast? (i.e. flights that represent a potential data entry error). Compute the air time a flight relative to the shortest flight to that destination. Which flights were most delayed in the air?

7. Find all destinations that are flown by at least two carriers. Use that information to rank the carriers.

8. For each plane, count the number of flights before the first delay of greater than 1 hour.

