---
title: "Using RMarkdown and ggplot"
author: "Seungmo Kim"
date: "4/23/2017"
output: 
  html_document: 
    keep_md: yes
---


install.packages("tidyverse")
library(tidyverse)

mpg

#### 3.2.4 Exercises

##### 1. Run ggplot(data = mpg) what do you see?
```{r}
# ggplot(data = mpg)
```
##### I don't get any plot.  I must specify the value of each axis and the type of plot.

##### 2. How many rows are in mtcars? How many columns?
```{r }
nrow(mtcars)
ncol(mtcars)
```

##### 3. What does the drv variable describe? Read the help for ?mpg to find out.
```{r}
?mpg
```
##### The drv variable describes the kind of driving system - f=front-wheel drive, r=rear wheel drive and 4=4 wheel drive.

##### 4. Make a scatterplot of hwy vs cyl.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy))
```

##### 5. What happens if you make a scatterplot of class vs drv. Why is the plot not useful?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = class))
```
##### Both variables are categorical.  In that case, a table is more informative than graph.
            
#### 3.3.1 Exercises

##### 1. What’s gone wrong with this code? Why are the points not blue?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```
##### The aesthetic color should be outside of the aesthetic parenthesis, to change the color of the points.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```

##### 2. Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?
```{r include=FALSE}
summary(mpg)
```
##### categorical variables: manufacturer, model, trans, drv, fl, and class 
##### continuous (vs. discrete) : displ, year, cly, cty, and hwy

##### 3. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?
```{r}
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, color=cty))
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, size=cty))
```
##### Continuous variables can be mapped to color and size on scaled gradient but not to shape.
```{r}
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, shape=cty))
```

##### 4. What happens if you map the same variable to multiple aesthetics?
```{r}
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, color=class, size=class))
```
##### plotted on both aesthetics

##### 5. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy, stroke = 1))
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy, stroke = 10))
```
##### The aesthetic stroke adjusts the size of the points in geom_point. 

##### 6. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?
```{r}
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, color=displ < 5))
```
#### color=displ < 5: the color shows if the value satisfies the given condition. 
```{r}
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, color=displ))
```
  
#### 3.5.1 Exercises

##### 1. What happens if you facet on a continuous variable?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(~cty)
# Too many facets may be generated.
```
##### 2. What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))
```
##### The empty cells means no data(observation) corresponding to variables indicated as facets. 

# 3. What plots does the following code make? What does . do?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```
##### facet_grid(drv ~ .) facets data by kind of driving system vertically while facet_grid(. ~ cyl) facets data by number of cylinders horizontally. Horizontal and verical placement of the facet may be chosen by flavor.

##### 4. Take the first faceted plot in this section:
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```
#### What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?
```
Using facet instead of color aesthetic to visualize the data can make trends within a variable more clear, but hide overarching trends in the entire data set. In a loarger data set it might be more benficial to facet the data to analyze trends in individual variables, and less important to use the color aesthetic to see overarching trends.


##### 5. Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol variables?
nrow and ncol define the number of rows or colums, and the direction, by hwich the data is faceted. as.table can also be used to change the layout of panels. In facet_grid(), nrow and ncol are defined by the variables used to define facets, with "." indicating one row or column.

##### 6. When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?
# facet_grid forms a matrix of panels defined by row and column facetting variables. It is most useful when we have two discrete variables, and all combinations of the variables exist in the data.
Puting the variable with the most unique number of levels in the rows can result in an oddly shaped figured.
Contact GitHub API Training Shop Blog About
© 2017 GitHub, Inc. Terms Privacy Security Status Help
