---
title: "Using ggplot2"
author: "Seungmo Kim"
date: "4/25/2017"
output: html_document
---


```{r include=FALSE}
library(tidyverse)
library(ggplot2)
mpg
```


### 3.2.4 Exercises


#### 1. Run ggplot(data = mpg) what do you see?
```{r eval=FALSE}
ggplot(data = mpg)
```
A plot is not generated. The value of each axis and the type of plot should be specified.


#### 2. How many rows are in mtcars? How many columns?
```{r }
nrow(mtcars)
ncol(mtcars)
```
number of rows: 32   number of caolumn: 11


#### 3. What does the drv variable describe? Read the help for ?mpg to find out.
```{r eval=FALSE}
?mpg
```
The drv variable describes driving system: f=front-wheel drive, r=rear wheel drive and 4=4 wheel drive.


#### 4. Make a scatterplot of hwy vs cyl.
```{r }
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy))
```


#### 5. What happens if you make a scatterplot of class vs drv. Why is the plot not useful?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = class))
```

Both variables are categorical.  In that case, a table is more informative than graph.


### 3.3.1 Exercises


#### 1. What’s gone wrong with this code? Why are the points not blue?
```{r eval=FALSE}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```
The aesthetic color should be outside of the aesthetic parenthesis to change the color of the points.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```


#### 2. Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?
```{r eval=FALSE}
summary(mpg)
```
Categorical variables: manufacturer, model, trans, drv, fl and class\
Continuous (vs. discrete) : displ, year, cly, cty and hwy


#### 3. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?
```{r eval=FALSE}
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, color=cty))
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, size=cty))
```
Continuous variables can be mapped to color and size on scaled gradient but not to shape.

```{r eval=FALSE}
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, shape=cty))
```


#### 4. What happens if you map the same variable to multiple aesthetics?
```{r warning=FALSE}
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, color=class, size=class))
```

plotted on both aesthetics


#### 5. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy, stroke = 1))
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy, stroke = 5))
```

The aesthetic stroke adjusts the size of the points in geom_point. 


#### 6. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?
```{r}
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, color=displ < 5))
```

color=displ < 5: The color varies depending on whether the value meets the given condition.
```{r eval=FALSE}
ggplot(mpg) + geom_point(mapping=aes(x=cyl, y=hwy, color=displ))
```



### 3.5.1 Exercises


#### 1. What happens if you facet on a continuous variable?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(~cty)
```

Too many facets may be generated and panels are difficult to compare.


#### 2. What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?
```{r eval=FALSE}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))
```
An empty cell means that there is no data (observation) corresponding to the variable represented by the facet.


#### 3. What plots does the following code make? What does . do?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

facet_grid(drv ~ .) facets data by kind of driving system vertically while facet_grid(. ~ cyl) facets data by number of cylinders horizontally. Horizontal and verical placement of the facet may be chosen by flavor.


#### 4. Take the first faceted plot in this section:
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

#### What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?  

Using faceting instead of the colour aesthetic helps us visualize the large data set 'more clear within a variable of interest'. However, it may not gives us a clear overal trends in the entire data set.


#### 5. Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol variables?

The arguments nrow and ncol set the number of rows and columns. We can place a label on one of the four sides by setting strip.position = c ("top", "bottom", "left", "right"). In facet_grid (), nrow and ncol can not be set, but facets can be placed in rows or columns by inserting '.'.


#### 6. When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?

Facet_grid forms a matrix of panels defined by row and column or facet variable. If we put a variable with a unique level in the row, an ambiguous (?) feature may be returned. This rule applies to most graphs or tables.

