---
title: "08302017_Kim.Seungmo"
output:
  html_document:
    keep_md: yes
---

```{r include=FALSE}
library(tidyverse)
```

20.4.6 Exercises

1. What does mean(is.na(x)) tell you about a vector x? What about sum(!is.finite(x))?
```{r}
x <- c(10, 3, NA, 5, 8, 1, NA)

is.na(x)
mean(is.na(x)) # FALSE -> 0, TRUE -> 1
#NA is a logical constant with a missing value indicator. 
#is.na() indicates which elements are missing.

!is.finite(x) # NA is not finite nor infinite and so is.finite(NA) -> FALSE and !is.finite(NA) -> TRUE (not equal to is.infinite(NA)!)
sum(!is.finite(x))
```

2. Carefully read the documentation of is.vector(). What does it actually test for? Why does is.atomic() not agree with the definition of atomic vectors above?
```{r}
# is.vector() returns TRUE if x is a vector of the specified mode having no attributes other than names. 
# is.atomic() returns TRUE if x is of an atomic type (or NULL).???
```

3. Compare and contrast setNames() with purrr::set_names().
```{r}
setNames( 1:4, c("foo", "bar", "baz") )
# a function to set the names on an object and returns the object.
#purrr::set_names( 1:4, c("foo", "bar", "baz"))
# a case wrapper for setNames, with stricter argument checking.
```

4. Create functions that take a vector as input and returns:

  The last value. Should you use [ or [[?
```{r}
vec <- c(1:4, NA, 6:9)

last_value <- function(x) {
  l <- length(x)
  x[l]
}
last_value(vec)
```
  The elements at even numbered positions.
```{r}
even_pos <- function(x) {
  l <- length(x)
  x[seq(l) %% 2 == 0]
}
even_pos(vec)
```
  Every element except the last value.
```{r}
no_last <- function(x) {
  l <- length(x)
  x[seq(l-1)]
}
no_last(vec)
```
Only even numbers (and no missing values).
```{r}
even_num <- function(x) {
  tempo <- x[sapply(x, "%%", 2) == 0]  
  tempo[!is.na(tempo)] # remove NAs
}
even_num(vec)

```

5. Why is x[-which(x > 0)] not the same as x[x <= 0]?
```{r}
x <- c(10, -3, NA, 5, 0)
which(x > 0) 
-which(x > 0) 
x[-which(x > 0)] #return all elements except x > 0, including NA

x[x <= 0] # should return all elements <= 0, not including NA. But include NA. Why?
```


6. What happens when you subset with a positive integer that’s bigger than the length of the vector? What happens when you subset with a name that doesn’t exist?
```{r}
x <- c(a=1, b=2, c=3, d=4, e=5)
x
x[1:10] # the portion beyond the length is filled with NAs
x[c("f", "g")] # return NAs(missing values)
```


20.5.4 Exercises

1. Draw the following lists as nested sets:

```{r}
#list(a, b, list(c, d), list(e, f))
```

```{r}
#list(list(list(list(list(list(a))))))
```

  
2. What happens if you subset a tibble as if you’re subsetting a list? What are the key differences between a list and a tibble?
```{r}
gr <- tibble(x = 1:4, y = rep(1:2, 2))
gr
gr[1]  #??????????
```

20.7.4 Exercises

1. What does hms::hms(3600) return? How does it print? What primitive type is the augmented vector built on top of? What attributes does it use?
```{r}
x <- hms::hms(3600) 
x # 3,600 s = 1 hr
unclass(x)
typeof(x)
attributes(x)
```

2. Try and make a tibble that has columns with different lengths. What happens?
```{r}
#tibble::tibble(x = 1:5, y = 4:1)
# Each column must have the same length.
```

3. Based on the definition above, is it ok to have a list as a column of a tibble?
```{r}

```


